### 2019-05-19 Plan_TeX/pages/work_plan.tex
Changes; - Restructuring of the archive folder - Added TeX version of paper notes - Added new papers for relevancy review - Included a script to generate fabricated target_key lists for benchmarking

\chapter{Work Plan}

\section{Project title/goal}

{
    \small
    "Investigating the feasibility of generating near-collisions for pEp TrustWords and its affect on security"

    \textbf{Points: } \\
    Use-case for TrustWords:
    \begin{itemize}
        \item Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
    \end{itemize}
}

\subsection{RFC drafts}
{
\small
\verb|draft-marques-pep-handshake-02|
\\
\textit{"Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.  Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."}

@@

\verb|draft-birk-pep-trustwords-00|
\\
In another draft document it also states:

\textit{"It is for further study, what minimal number of words (or entropy) should be required."}

This shows there is some sort of research gap.
}

@@

{
\small
\textbf{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}\\
Paper shows the usability of current schemes. The can be useful to show the need for trustwords and how they would fit in. Maybe even that the security needs improving for word based auth schemes?

@@

}

@@

\newpage
\section{Methods for creating similarities in words}

>>>>

\section{Work Plan}

\subsection{Project title/goal}

"Investigating the feasibility of generating near-collisions for pEp TrustWords and its affect on security"

\begin{itemize}
    \item Use-case for TrustWords: Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
\end{itemize}

\subsection{RFC drafts}
\subsubsection{draft-marques-pep-handshake-02}
``Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.  Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."

@@

\subsubsection{draft-birk-pep-trustwords-00}
In another draft document it also states:

``It is for further study, what minimal number of words (or entropy) should be required."

This shows there is some sort of research gap.

@@

\textbf{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}\\
Paper shows the usability of current schemes. The can be useful to show the need for trustwords and how they would fit in. Maybe even that the security needs improving for word based auth schemes?

@@

@@

\section{Methods for creating similarities in words}
